Effect of Election on Currency Fluctuation

### 2024-04-16 paper/paper.qmd
re-rendered the paper.pdf for peer review

## Data on Exchange Rate

The DEXCAUS [@Federal_Reserve] dataset includes the daily exchange rate between USD and CAD (base USD = 1) from 1971-01-04 to\
2024-03-29 (date the dataset is downloaded for the purpose of the paper). Raw data contains only the date and the corresponding exchange rate of the day. Exchange rate in this dataset is used as the estimate of this paper.

@@

exchange_inaug |>
  ggplot(aes(
    x = date,
    y = exchange_rate
  )) +
  geom_line() + theme_minimal() +
  labs(
    x = "Year",
    y = "Exchange Rate: USD to CAD (Base Currency: USD)",
    title = "Exchange Rate from 1971 to 2024"
  )
```

@@

In order to measure the effect that the population's faith to their country have on exchange rate, this paper focuses on one particular political event that will quickly change the population's expectation for their country in a short amount of time, the presidential election. Analysis will be focused on the election result announcement and the inauguration period (please see specific definition of the term inauguration period in the subset below @sec-inauguration). Data of past election results and inauguration dates are obtained through the US Census Bureau [@Census] and cross-referenced with Frank LaRose Ohio Secretary of State [@Ohio] for accuracy. The final dataset use the inauguration dates and political party information to determine the effect of having a new president on the USD exchange rate.

@@

## Final Dataset
The final dataset combines the date and exchange rate columns from the DEXCAUS [@Federal_Reserve] dataset and uses the inauguration week (constructed through the inauguration dates from the election results dataset, @sec-election). The column *Inauguration Period* has a value of 1 if the date is within the inauguration week and 0 otherwise. A new column *Change Party* is added, it receives a value of 1 if the political party of the new president is different from the previous president's and 0 otherwise.
```{r}
#| label: tbl-exchange_inaug
#| tbl-cap: Sample of the final dataset used for analysis
#| echo: false
sample_tbl <- exchange_inaug |> filter(date >= "1977-01-12" & date <= "1977-01-18")

@@

## Third discussion point

@@

# Additional data details

>>>>

@@

exchange_inaug |>
  ggplot(aes(
    x = date,
    y = exchange_rate
  )) +
  geom_line() + theme_minimal() +
  labs(x = "Year", y = "Exchange Rate: USD to CAD (Base Currency: USD)",
    title = "Exchange Rate from 1971 to 2024"
  )
```
## Data on Exchange Rate

The DEXCAUS [@Federal_Reserve] dataset includes the daily exchange rate between USD and CAD (base USD = 1) from 1971-01-04 to 2024-03-29 (date the dataset is downloaded for the purpose of the paper). Raw data contains only the date and the corresponding exchange rate of the day. Exchange rate in this dataset is used as the estimate of this paper.

@@

In order to measure the effect that the population's faith to their country have on exchange rate, this paper focuses on one particular political event that will quickly change the population's expectation for their country in a short amount of time, the presidential election. Analysis will be focused on the election result announcement and the inauguration period (please see specific definition of the term inauguration period in the subsection below @sec-inauguration). Data of past election results and inauguration dates are obtained through the US Census Bureau [@Census] and cross-referenced with Frank LaRose Ohio Secretary of State [@Ohio] for accuracy. The final dataset use the inauguration dates and political party information to determine the effect of having a new president on the USD exchange rate.

@@

## Final Dataset

The final dataset combines the date and exchange rate columns from the DEXCAUS [@Federal_Reserve] dataset and uses the inauguration week (constructed through the inauguration dates from the election results dataset, @sec-election). The column *Inauguration Period* has a value of 1 if the date is within the inauguration week and 0 otherwise. A new column *Change Party* is added, it receives a value of 1 if the political party of the new president is different from the previous president's and 0 otherwise.

```{r}
#| label: tbl-exchange_inaug
#| tbl-cap: Sample of the final dataset used for analysis
#| echo: false
sample_tbl <- exchange_inaug |> filter(date >= "1977-01-12" & date <= "1977-01-18")

@@

@@
